%% LaTeX2e class for student theses
%% sections/introduction/content.tex
%%
%% Karlsruhe University of Applied Sciences
%% Faculty of  Computer Science and Business Information Systems
%%
%% --------------------------------------------------------
%% | Derived from sdqthesis by Erik Burger burger@kit.edu |
%% --------------------------------------------------------

\chapter{Introduction}
\label{ch:Introduction}

% E-Mobility and Reservations...

\section{Target}
\label{ch:Introduction:sec:Target}

The fact that subsidies and other inducements provided by the manufacturers and the state itself lead to an further increasing amount of electric vehicles \cite{afshar_literature_2020} on the streets, the extension and management of the existing charging infrastructure will become an essential part of the overall satisfaction of the \acrfull{evu} community.
Especially management or administration processes ensuring a fair and well-regulated use of the single charging possibilities is a necessary feature most implementations are missing nowadays. 
The prime example addressing this problem, is the feature gap describing a reservation of a charging point in a specified time in the future. 

Therefore reservation process for electric vehicle management inside a reduced scenario, like a company car fleet, will be used as proof of concept to demonstrate the advantages in comparison to the first-come-first-serve principle. The following sections will describe the context of the required system with their given requirements and restrictions for the tasks. First of all, a definition for electric mobility will be given, which declares the given context and its parts.

\section{SAP SE}
\label{ch:Introduction:sec:SAP SE}
SAP SE, commonly referred to as SAP, is a multinational software corporation based in Walldorf, Germany. It is one of the world's leading enterprise software companies and is renowned for its innovative solutions that help businesses manage their operations effectively. It was founded in 1972 by Dietmar Hopp, Hasso Plattner, Claus Wellenreuther, Hans-Werner Hector, and Klaus Tschira. The company's primary goal was to develop standard application software for real-time business data processing and improve the way businesses managed their operations. Beside SAP S/4HANA and SAP ERP (Enterprise Resource PLanning), SAP offers a wirde range of enterprise software products and service and catering to various business needs and industries.
With its vast global presence of offices in more than 180 countries, SAP provides solutions to customer organizations of all sizes. From small and medium-sized enterprises to multinational corporations. Beside manufacturing industries the finance and healthcare sector, as well as, retail, utilities, and public sector organizations are covered by SAP products. SAP's commitment to innovation has led to continuous improvements and advancements in its software offerings. It has embraced emerging technologies such as artificial intelligence, machine learning, Internet of Things (IoT), and blockchain to enhance its products' capabilities and address the evolving needs of businesses.

% TODO: Add additional context for e-mobility solutions

